\documentclass[a4paper,11pt]{article}

\usepackage{amsthm,amsmath,amsfonts,epsfig,amssymb}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{xy}
\usepackage{graphics}
\xyoption{all}
\pagestyle{empty}

\def\spec#1{\mathrm{Spec}(#1)}
\def\bb#1{\mathbb{#1}}
\def\bZ{\mathbb{Z}}
\def\Zmd#1{\bZ/#1\bZ}
\def\mrm#1{\mathrm{#1}}
\def\Hom{\mathrm{Hom}}
\def\Ab{\mathrm{Ab}}
\def\Mod#1{#1\mathrm{Mod}}
\def\PSh{\mathrm{PSh}}
\DeclareMathOperator{\colim}{colim}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Spec}{Spec}
\newcommand*\pp{{\rlap{\('\)}}}

\begin{document}


{\small Algebraic geometry \hfill September 14, 2022 \\}
\begin{center}
\Huge Exercises 2
\end{center}

\vskip0.6cm
\footnote{find also the exercises on https://github.com/iamcxds/AG-exercise, you can skip the question with * if it is difficult.}
Here we only discuss the underlying topological space of the spectrum. And the maximal spectrum is the subspace of maximal ideals.
\begin{enumerate}[1.]
\item 
\begin{enumerate}
    \item Show that the maximal spectrum of $\Spec\bb{C}[x]$ is the complex plane $\bb{C}$ with cofinite topology.
    \item Show that the maximal spectrum of $\Spec \bb{R}[x]$ is $\bb{C}$ quotiented by a $\Zmd{2}$ action with cofinite topology.
    \item Show that the maximal spectrum of $\Spec \bb{C}[x,y]/(x^2+y^2+1)$ is 
    \[\{(s,t)\in \bb{C}^2|s^2+t^2+1=0\}\] with cofinite topology. Then show that there is an isomorphism $i: \Spec \bb{C}[x,x^{-1}] \to \Spec \bb{C}[x,y]/(x^2+y^2+1)$
    \item* Show that the maximal spectrum of $\Spec \bb{R}[x,y]/(x^2+y^2-1)$ consists of 
    \[\{(s,t)\in \bb{R}^2|s^2+t^2=1\} \mrm{ \ and\ } \{ l\in lines(\bb{R}^2)|l\mrm{ \ not \ intersect\ with\ } s^2+t^2=1\} \] 
    with cofinite topology.
    
\end{enumerate}
\item Let ring $ A:= \bZ[x_{11},\ldots,x_{1n},\ldots,x_{nn},\iota]/(\iota\mrm{det}(x)-1) $ where $\mrm{det}(x)$ is the polynomial of determinant and let $\mrm{GL}_n$ be $ \Spec A $. Show that for ring $R$ \[\mrm{GL}_n(R):=\Hom_{Ring}(A, R)\cong 
\{\mrm{ invertible\ matrices\ with\ coefficient\ } R\} \]
\item Let $k$ be a field, find out what are the prime spectra of the following rings, and the open(or closed) sets of Zariski topology.
\begin{enumerate}
    \item  $\Spec k[x]/(x^2)$
    \item  $\Spec k[[x]]$( where $k[[x]] := \lim_n k[x]/(x^n)$ is the formal polynomial ring)
    \item  $\Spec k[x]_{(x)}$
    \item $\Spec \Zmd{m}$
    \item*  $\Spec \bZ[x]$
\end{enumerate}



\end{enumerate}


\end{document}