\documentclass[a4paper,11pt]{article}

\usepackage{amsthm,amsmath,amsfonts,epsfig,amssymb}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{xy}
\usepackage{graphics}
\xyoption{all}
\pagestyle{empty}

\def\spec#1{\mathrm{Spec}(#1)}
\def\bb#1{\mathbb{#1}}
\def\bZ{\mathbb{Z}}
\def\Zmd#1{\bZ/#1\bZ}
\def\mrm#1{\mathrm{#1}}
\def\Hom{\mathrm{Hom}}
\def\Ab{\mathrm{Ab}}
\def\Mod#1{#1\mathrm{Mod}}
\def\PSh{\mathrm{PSh}}
\DeclareMathOperator{\colim}{colim}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Spm}{Spm}
\DeclareMathOperator{\Spec}{Spec}

\newcommand*\pp{{\rlap{\('\)}}}

\begin{document}


{\small Algebraic Geometry
\footnote{find also these exercises on https://github.com/iamcxds/AG-exercise, you can skip a question with * if it is difficult.}
 \hfill November 30, 2022 \\}
\begin{center}
\Huge Exercises 8
\end{center}


\vskip0.6cm


\begin{enumerate}[1.]

\item (Functor of points)
Recall the Yoneda lemma: An object $X$ is decided by the functor $\Hom(-, X)$. Conversely, from a functor $F$, we can try to find the object that represents it. (e.g. we have seen that the line bundles with $n+1$ section over $X$ is represented by $\bb{P}^n$)
\begin{enumerate}
    \item For a set $S$, let $P(S)$ be the set of subsets. Can you find the set that represents $P$? (i.e. find such set $B$ s.t. $P(S)\cong \Hom_{\mrm{Set}}(S,B)$) 
    \item For a polynomial $f\in \bb{Z}[x,y]$. Let $h_f(\Spec R)=\{(x,y)\in R, f(x,y)=0\}$. Can you find the scheme that represents $h_f$?
    \item For any scheme $X$, denote $X(R)$ for the $\Hom_{\mrm{Sch}}(\Spec R, X)$. which is the functor of points. If $X$ is a variety over an algebraically close field $k$, then show that $X(k)$ corresponds to the set of close points.
    \item If $X$ is a variety over $\bb{C}$, then show that there is a $\bb{Z}/2\bb{Z}$ action on $X(\bb{C})$, And the fix points are corresponds to $X(\bb{R})$
    \item Show that $X\times_Z Y(R)\cong X(R)\times_{Z(R)} Y(R)$. So we can define the fiber product $X\times_Z Y$as the scheme represents $  X(R)\times_{Z(R)} Y(R) $. But how can we find such a scheme?\footnote{see more on https://stacks.math.columbia.edu/tag/01JF}
    
\end{enumerate}
\item* For topological space $X$, show that $X$ is proper (i.e. $X\times Y\to Y$ is closed for any $Y$) iff $X$ is compact. (More generally, for proper map $f:X\to Y$, for $y\in Y$, we have the fibre $f^{-1}(y)$ is compact)
\item* Recall the fact that holomorphic functions on compact Riemann surfaces are constant. Let $k$ be an algebraically closed field, and let  $X$ be a connected reduced proper $k$-scheme. Then $\mathcal{O}_X(X)=k$.
\end{enumerate}





\end{document}